Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-12-03 neurips-20/tikz/abstain-bounds-fsd-flat.tex
Adding COLT formatting files

%abstain alpha = 1/2
\begin{tikzpicture}
\draw (2,0) -- (-2,0) -- (0,3.46) -- cycle;
%label outcomes
\node at (-9/4, 0) {$p_1$};
\node at (2/5, 3.25) {$p_2$};
\node at (9/4, 0) {$p_3$};
%level sets
\draw[fill = blue, fill opacity = 0.1] (-1, 1.73) -- (1, 1.73) -- (0, 3.46) -- cycle; \node at (0, 1.73*1.35) {\footnotesize$2$};
\draw[fill = green, fill opacity = 0.1] (2,0) -- (1, 1.73) -- (0,0) -- cycle;
\node at (1, 1.73*0.4) {\footnotesize$3$};
\draw[fill = yellow, fill opacity = 0.1] (-2,0) -- (-1, 1.73) -- (0,0) -- cycle;
\node at (-1, 1.73*0.4) {\footnotesize$1$};
\draw[fill = gray, fill opacity = 0.1] (1,1.73) -- (-1, 1.73) -- (0,0) -- cycle;
\node at (0, 1.73*0.35) {\footnotesize$\bot$};
%uniform distribution
\node at (0, 1.73*0.65) {\textbullet};
\draw[fill=gray, fill opacity = 0.25, dashed] (0,1.73 * 0.65) circle (0.2);
\end{tikzpicture}

%abstain alpha = 1/2
\begin{tikzpicture}
\draw (2,0) -- (-2,0) -- (0,3.46) -- cycle;
%label outcomes
\node at (-9/4, 0) {$p_1$};
\node at (2/5, 3.25) {$p_2$};
\node at (9/4, 0) {$p_3$};
%level sets
\draw[fill = blue, fill opacity = 0.1] (-1, 1.73) -- (1, 1.73) -- (0, 3.46) -- cycle; \node at (0, 1.73*1.35) {\footnotesize$2$};
\draw[fill = green, fill opacity = 0.1] (2,0) -- (1, 1.73) -- (0,0) -- cycle;
\node at (1, 1.73*0.4) {\footnotesize$3$};
\draw[fill = yellow, fill opacity = 0.1] (-2,0) -- (-1, 1.73) -- (0,0) -- cycle;
\node at (-1, 1.73*0.4) {\footnotesize$1$};
\draw[fill = gray, fill opacity = 0.1] (1,1.73) -- (-1, 1.73) -- (0,0) -- cycle;
\node at (0, 1.73*0.35) {\footnotesize$\bot$};
%uniform distribution
\node at (0, 1.15333) {\textbullet};
\draw[loosely dotted,thick, opacity=0.6] (0, -0.5) -- (0,3.6);
\draw[loosely dotted,red, thick] (-1, -0.576666) -- (1., 2.8333);
\draw[loosely dotted, blue, thick] (-1.8, 1.15333) -- (1.8, 1.15333);

>>>>

%abstain alpha = 1/2
\begin{tikzpicture}
\draw[opacity = 0.2] (2,0) -- (-2,0) -- (0,3.46) -- cycle;
%label outcomes
\node at (-9/4, 0) {$p_1$};
\node at (2/5, 3.25) {$p_2$};
\node at (9/4, 0) {$p_3$};
%level sets
\draw[fill = blue, fill opacity = 0.1, opacity = 0.2] (-1, 1.73) -- (1, 1.73) -- (0, 3.46) -- cycle; \node at (0, 1.73*1.35) {\footnotesize$2$};
\draw[fill = green, fill opacity = 0.1, opacity = 0.2] (2,0) -- (1, 1.73) -- (0,0) -- cycle;
\node at (1, 1.73*0.4) {\footnotesize$3$};
\draw[fill = yellow, fill opacity = 0.1, opacity = 0.2] (-2,0) -- (-1, 1.73) -- (0,0) -- cycle;
\node at (-1, 1.73*0.4) {\footnotesize$1$};
\draw[fill = gray, fill opacity = 0.1, opacity = 0.2] (1,1.73) -- (-1, 1.73) -- (0,0) -- cycle;
\node at (0, 1.73*0.35) {\footnotesize$\bot$};
%uniform distribution
\node at (0, 1.73*0.65) {\textbullet};
\draw[fill=gray, fill opacity = 0.25, dashed] (0,1.73 * 0.65) circle (0.2);

%p = (1/4, 1/4, 1/2)
\node at (0.5, 0.865) {{\color{blue}\textbullet}};
\draw[thick, dashed, blue] (0, 0) -- (1,1.73);

%abstain alpha = 1/2
\begin{tikzpicture}
\draw[opacity = 0.2] (2,0) -- (-2,0) -- (0,3.46) -- cycle;
%label outcomes
\node at (-9/4, 0) {$p_1$};
\node at (2/5, 3.25) {$p_2$};
\node at (9/4, 0) {$p_3$};
%level sets
\draw[fill = blue, fill opacity = 0.1, opacity = 0.2] (-1, 1.73) -- (1, 1.73) -- (0, 3.46) -- cycle; \node at (0, 1.73*1.35) {\footnotesize$2$};
\draw[fill = green, fill opacity = 0.1, opacity = 0.2] (2,0) -- (1, 1.73) -- (0,0) -- cycle;
\node at (1, 1.73*0.4) {\footnotesize$3$};
\draw[fill = yellow, fill opacity = 0.1, opacity = 0.2] (-2,0) -- (-1, 1.73) -- (0,0) -- cycle;
\node at (-1, 1.73*0.4) {\footnotesize$1$};
\draw[fill = gray, fill opacity = 0.1, opacity = 0.2] (1,1.73) -- (-1, 1.73) -- (0,0) -- cycle;
\node at (0, 1.73*0.35) {\footnotesize$\bot$};
%uniform distribution
\node at (0, 1.15333) {\textbullet};
\draw[loosely dotted,thick, opacity=0.6] (0, -0.5) -- (0,3.6);
\draw[loosely dotted,red, thick] (-1, -0.576666) -- (1., 2.8333);
%\draw[loosely dotted, blue, thick] (-1.8, 1.15333) -- (1.8, 1.15333);

%p = (1/4, 1/4, 1/2)
\node at (0.5, 0.865) {{\color{blue}\textbullet}};
\draw[thick,blue] (0, 0) -- (1,1.73);
